\documentclass[11pt]{article}
\usepackage{pslatex}
\usepackage{exam,amssymb,amsmath}
\pagestyle{fancy}
\newcommand{\pd}[2]{\frac{\partial (#1)}{\partial (#2)}}
\newcommand{\Jaco}[2]{\frac{\partial (#1)}{\partial (#2)}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\paper{Roll No.
	%\centering
		\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
			& & & & & & &  \\
			\hline
		\end{tabular}
}
%\rollnobox
\title{First Semester}
\subject{M.Sc. Applied Mathematics}
\coursename{Foundation of Cryptography and Security}
\coursecode{~MA-008}
\maxmarks{50}
\time{2:00}
\semester{Mid Semester}
\year{September, 2013}
%\answersheettop
%\subjecttwo{Paper Id: 0934}
\note{Attempt \textbf{all} the questions. Be concise and adopt mathematical approach.}
\begin{document} 
\begin{questions}
\question Attempt ALL parts of the following: \marks{$5 \times 2=10$}
	\begin{enumerate}
	\item Find gcd(174, 204).
	\item Find all the integral solutions of $174x + 204y = 18$.
	\item If $d = gcd(a, b)$, then what is the gcd of $a^n$ and $b^n$? What will be the gcd of $a^m$ and $b^n$?
	\item Encrypt MID SEMESTER EXAMINATIONS by using Caeser Cipher system.
	\item Do the cryptanalysis of the message ``ilza vm sbjr'' (without quotes).
	
	\end{enumerate}
\vspace{-0.2cm}
\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item Describe Euclid's Algorithm. If $a = 66$ and $b = 26$ then find $gcd(a,b)$ and also express the $gcd(a,b)=ax+by$
\item Show that there are infinitely many primes.
\end{enumerate}
\vspace{-0.2cm}
\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item State the Chinese Remainder Theorem. Solve the following system of linear congruences 

$x \equiv 2 \mod 6$, $x \equiv 1 \mod 5$, $x\equiv 3 \mod 7$.
\item Solve the system of linear congruences $5x \equiv 1 \mod 6$, $3x \equiv 2 \mod 5$, $4x \equiv 5 \mod 7$.
\end{enumerate}
\vspace{-0.2cm}
\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item Define a cryptosystem. What are symmetric cryptosystems and  asymmetric  cryptosystems? 
\item What is the Key Management Problem? What are the known possible solutions?
\end{enumerate}
\vspace{-0.2cm}
\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item What do you understand with attacks. Describe various attacks. (You may take help of diagrams if required.)
\item Describe Diffie-Hellmen Key agreement protocol? Also show that this is insecure against Man-in-Middle Attack?
\end{enumerate}


\end{questions}
\end{document}
 
