\documentclass[11pt]{article}
\usepackage{pslatex}
\usepackage{exam,amssymb}
\pagestyle{fancy}
\newcommand{\pd}[2]{\frac{\partial (#1)}{\partial (#2)}}
\newcommand{\Jaco}[2]{\frac{\partial (#1)}{\partial (#2)}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\paper{Roll No.
	%\centering
		\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
			& & & & & & &  \\
			\hline
		\end{tabular}
}
%\rollnobox
\title{First Semester}
\subject{M.Sc. Applied Mathematics}
\coursename{Linear Algebra}
\coursecode{~MA-401}
\maxmarks{50}
\time{2:00}
\semester{Mid Semester}
\year{September, 2013}
%\answersheettop
%\subjecttwo{Paper Id: 0934}
%\note{Attempt \textbf{all} the questions.}
\begin{document} 
\begin{questions}
\question Attempt ALL parts of the following: \marks{$5 \times 2=10$}
	\begin{enumerate}
	\item Find the dimension of the vector space $\C(\R)$ (with usual notations).
	
	\item Is vector $(3,-1,0,-1)$ spanned by the vectors $(2,-1,3,2)$, $(-1,1,1-3)$, and (1,1,9,-5)?
 \item Find three vectors in $\R^3$ which are linearly dependent, and are such that any two of them are linearly independent.
	\item Is the mapping $T: \R^2 \rightarrow \R^2$ linear where $T(x,y) = (\sin x, y)$.
	\item Find the range, rank, null space, and nullity for the zero transformation and the identity transformation on a finite dimensional vector space $V$.
	\end{enumerate}

\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item Let $V$ be the set of pairs $(x,y)$ of real numbers and let $\F$ be the field of real numbers. Given
$(x_1,y_1) + (x_2 + y_2) = (x_1+x_2 , 0) $ and $c(x,y) = (cx,0)$. Is $V$, with these operations, a vector space?
\item Prove that number of elements in a basis of a vector space $V$ are unique.
\end{enumerate}

\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item Let $V$ be a vector space over the field $F$. Show that, the intersection of any two subspaces of $V$ is subspace of $V$.
	\item Show that the vectors $(1,0,-1)$, $(1,2,1)$, and $(0,-3,2)$ form a basis for $\R^3$. Express each of the standard basis vectors as linear combinations of these three vectors.
\end{enumerate}

\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item State and Prove Rank Nullity Theorem.
	\item If $T$ be the unique linear operator on $\C^3$ for which $T(e_1)=(1,0,i)$, $T(e_2)=(0,1,1)$, ${T(e_3)=(i,1,0)}$. Is $T$ invertible?
\end{enumerate}
%\newpage
\item Attempt ALL parts of the following: \marks{$2 \times 5= 10$}

If $T$ be the linear transformation from $\R^3$ into $\R^2$ defined by $T(x,y,z)=(x+y, 2z-x)$. Then
\begin{enumerate}
\item If $B$ is the standard ordered basis for $\R^3$ and $B'$ is the ordered basis for $\R^2$, what is the matrix of $T$ relative to pair $B,\,B'$ .
\item If $B = \{(1,0,-1),(1,1,1),(1,0,0)\}$  and $B'=\{(0,1),(1,0)\}$, what is the matrix of $T$ relative to pair $B,\,B'$.	
\end{enumerate}
\end{questions}
\end{document}
 
