%&pdflatex
\documentclass[11pt]{article}
\usepackage{pslatex}
\usepackage{exam,amssymb,amsmath}
\pagestyle{fancy}
\newcommand{\pd}[2]{\frac{\partial (#1)}{\partial (#2)}}
\newcommand{\Jaco}[2]{\frac{\partial (#1)}{\partial (#2)}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\paper{Roll No.
        %\centering
                \begin{tabular}{|c|c|c|c|c|c|c|c|}
                \hline
                        & & & & & & &  \\
                        \hline
                \end{tabular}
}
%\rollnobox
\title{First Semester}
\subject{M.Sc. Applied Mathematics}
\coursename{Fundamentals of Computer Programming}
\coursecode{~MA-413}
\maxmarks{50}
\time{2:00}
\semester{Mid Semester}
\year{September, 2013}
%\answersheettop
%\subjecttwo{Paper Id: 0934}
\note{Attempt \textbf{all} the questions. }
\begin{document} 
\vspace{-1cm}
\begin{questions}
\question Attempt ALL parts of the following: \marks{$5 \times 2=10$}
        \begin{enumerate}
\item What are the major differences between main memory and external memory?                                                   
\item Write the name and purpose of $<<$ and $>>$ operators.                            
\item A program runs without any errors being reported but outputs results that are wrong, what type of error is likely to have caused this? Illustrate.                   
\item To what do the following expressions evaluate? $(17/3), (17\%3), (1/2), (1/2)*(x+y)$
\item Write the name and syntax of any two decision statements.
        
        \end{enumerate}
\vspace{-0.2cm}
\question Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item   What do you understand with data type in C++. Please discuss any four data types.
\item Write a simple program to illustrate variables, keyword, data types, operators etc. used in C++                                                                      
\end{enumerate}
\vspace{-0.2cm}
\question  Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\vspace{-0.2cm}
\begin{enumerate}                        
\item
Correct the program given below -                                                       
                     \begin{verbatim}
                        include <iostream.h>
                        int main ()
                        {
                                float a =5; 
                                int b(2);
                                int result;

                                a = a + 1;
                                result = a - b;
                                cout << result;
                        }
                \end{verbatim}
        \item Write a program to evaluate the fuel consumption of a car. The
reading at the start and end of the journey should be read, and also
the fuel level in the tank at the start and end of the journey. Calculate
fuel used, meters travelled, and \textsl{a}hence the overall fuel consumption in
meters travelled per 1000 litre of fuel.
\end{enumerate}

\question Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item A program is required which will read in the breadth and height of a
rectangle and which will output the area and the length of the perimeter of the rectangle. Write an algorithm for this problem.
Write C++ code too.
\item   Percentage marks attained by a student in three exams are to be entered to a computer. An indication of Pass or Fail is given out after
the three marks are entered. The criteria for passing are as follows:
A student passes if all three examinations are passed. Additionally a
student may pass if only one subject is failed and the overall average
is greater than or equal to 50. The pass mark for an individual subject
is 40.
Write a C++ program to implement this task..                                          
\end{enumerate}
\vspace{-0.2cm}

\question Attempt ALL parts of the following: \marks{$2 \times 5= 10$}
\begin{enumerate}
\item Write a program using  decision statement “if and if…then…else”  \item 
        Correct the syntax errors in the following C++ program:
        \begin{verbatim}
        include iostream.h
        Main();
        {
        Float x,y,z;
        cout < "Enter two numbers "; cin >> a >> b
        cout << 'The numbers in reverse order are'
        << b,a;
        }
        \end{verbatim}
\end{enumerate}
\vspace{-0.2cm}
\end{questions}
\end{document}
 
